---
title: "Tidy Tuesday Week 25"
author: "Talia"
date: "6/16/2021"
output: 
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)     
library(lubridate)     
library(ggthemes)      
theme_set(theme_minimal()) 
```

```{r}
# Read in the tweets data for the week - this is choice #1

tweets <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-15/tweets.csv')
```

If you choose to replicate a graph, read in the data this way:

```{r}
# Read in the data for the week
georgia_pop <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-16/georgia_pop.csv')
census <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-16/census.csv')
furniture <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-16/furniture.csv')
city_rural <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-16/city_rural.csv')
income <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-16/income.csv')
freed_slaves <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-16/freed_slaves.csv')
occupation <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-16/occupation.csv')
conjugal <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-16/conjugal.csv')
```

This week's data is about the W.E.B DuBois challenge which was held earlier this year. You have two choices today: 1. You can analyze the tweet data for this week. 2. Try to replicate one of W.E.B. DuBois's graphs. 

For choice #1, read more about the data, including definitions of variables, [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-06-15/readme.md). 

```{r}
tweets %>% 
  mutate(date = date(datetime)) %>%
  group_by(date) %>% 
  summarize(ntweets = n(),
            verified) %>% 
  filter(!is.na(verified)) %>% 
  ggplot(mapping = aes(x = date,
                       y = ntweets,
                       color = verified)) + 
  geom_line(lwd = 0.75) + 
  theme_classic() +
  theme(plot.title.position = "plot",
        plot.caption.position = "plot",
        plot.title = element_text(family = "mono")) +
  scale_color_manual(values = c("deepskyblue3", "goldenrod3")) +
  labs(x = "", 
       y = "", 
       title = "TOTAL TWEETS OVER TIME",
       color = "Verified",
       caption = "Plot created by Talia C, data from Tweets")
```

For choice #2, you will attempt to recreate visualizations made by W.E.B. DuBois for the 1900 Paris Exposition.

```{r}
#pivot data to be longer 
conjugal_long <- conjugal %>% 
  pivot_longer(cols = c("Single", "Married", "Divorced and Widowed"),
               names_to = "marriagestatus",
               values_to = "proportion")

#replicating W.E.B. DuBois Graph
conjugal_long %>% 
  ggplot(mapping = aes(x = proportion,
                       y = fct_relevel(Population, levels = c("Negroes", "Germany")), 
                       fill = marriagestatus)) +
  geom_col(position = "stack") + 
  facet_wrap(vars(Age), 
             ncol = 1) + 
  theme(legend.position = "top",
        plot.background = element_rect(fill = "#E5D5C5"),
        plot.title = element_text(family = "mono", hjust = 0.5),
        panel.grid = element_blank())+
  scale_fill_manual(values = c("#537763", "#FFBE03", "#E73150")) +
  labs(x = "", 
       y = "", 
       title = "CONJUGAL CONDITIONS",
       fill = "",
       caption = "Plot created by Talia C, data from W.E.B. DuBois")
```
